The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-19 src/ms.tex
acknowledgements from authorship form

>>>>

JAA-M acknowledges funding support from Macquarie University through the
International Macquarie University Research Excellence Scholarship (`iMQRES').
AB was supported by the Lend\"ulet Program of the Hungarian Academy of Sciences,
project No. LP2018-7, and the KKP-137523 `SeismoLab' \'Elvonal grant of the
Hungarian Research, Development and Innovation Office (NKFIH).
MB gratefully acknowledges support by the ANID BASAL project FB210003 and the
FONDECYT regular grant 1211000.
FDE acknowledges funding through the H2020 ERC Consolidator Grant 683184, the
ERC Advanced grant 695671 ``QUENCH'' and support by the Science and Technology
Facilities Council (STFC).
SG made contributions to Astropy a part of the Google Summer of Code 2021.
SG acknowledges some intellectual support from the CCAD-UNC-NOVA.
Funding for the Stellar Astrophysics Centre is provided by The Danish National
Research Foundation (Grant agreement no.: DNRF106).
NK acknowledges support from the MIT Pappalardo fellowship.
KAO acknowledges support by the European Research Council (ERC) through Advanced
Investigator grant to C.S. Frenk, DMIDAS (GA 786910).
CP is supported by the Canadian Space Agency under a contract with NRC Herzberg
Astronomy and Astrophysics.
SP has been supported by Spanish MINECO-FEDER grant RTI2018-096188-B-I00
JPG acknowledges funding support from Spanish public funds for research from
project PID2019-107061GB-C63 from the ``Programas Estatales de Generaci\'on de
Conocimiento y Fortalecimiento Cient\'ifico y Tecnol\'ogico del Sistema de I+D+i
y de I+D+i Orientada a los Retos de la Sociedad,'' as well as from the State
Agency for Research of the Spanish MCIU through the ``Center of Excellence
Severo Ochoa'' award to the Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a
(SEV-2017-0709).
NS acknowledges support from the National Science Foundation through the
Graduate Research Fellowship Program under Grant 1842402. Any opinions,
findings, and conclusions or recommendations expressed in this material are
those of the authors and do not necessarily reflect the views of the National
Science Foundation.
Supported by the international Gemini Observatory, a program of NSF's NOIRLab,
which is managed by the Association of Universities for Research in Astronomy
(AURA) under a cooperative agreement with the National Science Foundation, on
behalf of the Gemini partnership of Argentina, Brazil, Canada, Chile, the
Republic of Korea, and the United States of America.
Parts of this research was supported by the Australian Research Council Centre
of Excellence for All Sky Astro-physics in 3 Dimensions (ASTRO 3D), through
project number CE170100013.
DS is supported by STFC grant ST/S000240/1.
NS acknowledges the support of the Science and Engineering Research Council of
Canada (NSERC) Canadian Graduate Scholarship — Doctoral Program, [funding
reference numbers CGSD — 54721 — 2020].
